---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# NaturePHDSurvey

<!-- badges: start -->
![R-CMD-check](https://github.com/jflint21/NaturePHDSurvey/workflows/R-CMD-check/badge.svg)
<!-- badges: end -->

The goal of NaturePHDSurvey is to provide a relatively curated interface with the set of responses to the 2019 Nature survey of current PhD candidates.

## Installation

You can install the released version of NaturePHDSurvey from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("NaturePHDSurvey")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jflint21/NaturePHDSurvey")
```
## Example 1: Do older PhD students experience more bullying? 

```{r example1, message = FALSE}
library(NaturePHDSurvey)
library(tidyverse)

PhD_Survey_ds_1 <- NaturePHDSurvey %>%
  group_by(age, discriminated) %>%
  summarize(n = n()) %>%
  pivot_wider(names_from = discriminated, values_from = n) %>%
  mutate(prop_discriminated = Yes / (Yes + No)) %>%
  select(age, prop_discriminated)

knitr::kable(PhD_Survey_ds_1, 
             digits = 2, 
             align = "c",
             col.names = c("Age Group", "Proportion experiencing bullying"))
```

The youngest students experience the lowest rate of bullying, at about $13.5\%$.

PhD students aged 35 to 55 experience significantly more bullying than their younger (or older) peers, by about 2-2.5 times.

By age 65 or older, bullying rates return to those seen for young students (18-24 years of age).

## Example 2: Is there an association between hours worked and satisfaction? 

```{r example2}
PhD_Survey_ds_2 <- NaturePHDSurvey %>%
  group_by(hours) %>%
  summarize(satisfaction = mean(satisfaction))

knitr::kable(PhD_Survey_ds_2, 
             digits = 1,
             align = "c",
             col.names = c("Typical weekly hours", "Satisfaction"))
```

Self-reported satisfaction is highest among those PhD students working 21-30 hours per week.

The lowest satisfaction rates are reported by those students working less than 11 hours per week.

Breaking the general downward trend in satisfaction as work hours increase beyond 21-30 hours per week, there is a spike in satisfaction among those students working more than 80 hours per week.
